Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-01-21 lloveras_2020.tex
Version 1.0

\begin{abstract}
Observational techniques play an essential role in advancing our understanding of the physics of the solar corona, providing in particular validation data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere. Solar rotational tomography is currently the sole observational technique that provides a 3D quantitative description of the solar corona at a global scale. Based on \diego{extreme ultraviolet} data of space borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$. We carry out a study of the corona combining {DEMT} reconstructions with MHD simulations using the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework. Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the declining} phase of SC 24. The 3D tomographic and MHD models are analysed and compared in distinct coronal magnetic structures. {We report in quantitative detail on the 3D termodinamic structure of the inner corona as revealed by the DEMT analysis. We show in particular the existence of diverse types of temperature structures in the low and mid latitudes of the streamer belt, and that the heating energy required to keep them stable may be accounted for by Alfvén waves. We show that the latest version of the AWSoM model results agree with DEMT reconstructions to within a $\approx 20\%$ accuracy or better. We report on aspects of the AWSoM model that could be improved to better reproduce the DEMT results, in particular concerning the source region of the fast/slow solar winds.}
\end{abstract}

@@

Being the \diego{region} where the solar atmosphere is \diego{heated, solar wind accelerated}, and where impulsive events such as solar flares and coronal mass ejections are energized, observation and modeling of the solar corona are tasks of great relevance to improve our understanding of the Sun-Earth environment. To advance our knowledge of the physics of the solar corona, as well as to improve its three-dimensional (3D) models, information derived from observational data plays a key role. Solar rotational tomography (SRT) is currently the sole observational technique able to provide a quantitative empirical description of the 3D distribution of some fundamental plasma parameters of the solar corona at a global scale.

\noindent\notebyalbert{Here we will put in a couple of paragraphs summarizing what SRT and DEMT are, including references and defining the accronyms in the process. We should refer to minima in particular. We should mention the instruments and missions we use as data for DEMT, and define their accronyms too. Also one paragraph on the SWMF/AWSoM model, including references and defining the accronyms on the way.}

\diego{To study the global coronal 3D structure, SRT proved to be a powerful tool. Based on solar rotation, allow instruments to compile a time series of images that cover the entire corona collecting data from all lines of sight.} In particular, differential emission measure tomography (DEMT), based on time-series of extreme ultraviolet (EUV) images, allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the \diego{quiet-Sun low corona at a global scale.} The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}. Using solar rotation time series of EUV images taken in channels sensitive to different temperatures, the technique allows calculation of 3D maps of electron density and temperature in the heliocentric height range $1.0\,\mrsun$ to $1.2\,\mrsun$ as summarized in Section \ref{demt}. The reader may refer to the recent review by \citet{vasquez_2016} that summarizes the DEMT technique.

\diego{
A combination of the DEMT and global magnetic models has provided useful insight into the 3D thermodynamical structure of the global quiet-Sun corona. In previous works, DEMT has been combined with a potential field source surface (PFSS) model such as \citet{huang_2012}, \citet{nuevo_2013} and \citet{nuevo_2015}. Recently, \citet{lloveras_2017} combined DEMT with PFSS to study the thermodynamic of the last two solar minima along magnetic field lines and selecting different magnetic structures and \citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona throgh PFSS magnetic lines.}

\diego{The Alfvén Wave Solar Model (AWSoM) of the Space Weather Modeling Framework model is constantly validated with observations as new improvements are implemented, in particular, \citet{oran_2015} used DEMT to validate the model in the low corona. More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT resutls in a globally fashion, obtaining an agreement within 20\%.
We used AWSoM results with two purposes. On the one hand to provide thermodynamic results to be contrasted with DEMT, and on the other hand to provide magnetohydrodynamic (MHD) coronal magnetic field model that is used to study thermodynamics along field lines.
}\\
We carry out a quantitatively detailed comparative \diego{DEMT/AWSoM} analysis of the Carrington Rotation (CR)-2082 during the Solar Cycle (SC) 23/24 minimum and CR-2208 during the declining fase of SC 24. To study CR-2082 data taken by the \textit{Extreme UltraViolet Imager Behind} \diego{(EUVI-B \citep{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) was used \diego{for DEMT, and Global Oscillation Network Group (GONG) magnetogram as the only input for AWSoM}, while data taken by the \textit{Atmospheric Imaging Assembly instrument} \diego{(AIA \citep{lemen_2012})}, on board the \textit{Solar Dynamics Observatory} (SDO) mission was used to study CR-2208 \diego{for DEMT, and Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG magnetograms for AWSoM}.

\diego{
Section \ref{demt} and \ref{awsom} summarizes DEMT technique, AWSoM model, instruments, and datasets we used. Section \ref{trace} explains the technique that is used to trace the thermodynamic results along the field lines. Section \ref{energia} details the energy model and the loop integrated quantities that are part of the comparative analysis. In Section \ref{demt_res} the quantitative comparative analysis of both rotations using DEMT is described and in Section \ref{awsom_res} AWSoM results are related to the one of DEMT. Finally in Section \ref{discu} summarizes and discusses the main conclusions of this analysis, and anticipates further planned work.
}
\\
%\diego{El parrafo de abajo lo pondria en la seccion 2.1}\\
%In DEMT, the low corona in the height range $1.0-1.25\,\mrsun$ is discretized in a spherical computational grid. The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions. The cadence of the data time-series is set to 6\,hr. The main product of the technique is the local DEM (LDEM) at each volxel, a measure of the temperature distribution of the plasma contained in it.

@@

{The solution of the tomographic problem involves a very large sparse matrix. Such type of inversion problems are characterized by spurious high-frequency artifacts in the solution, which can be mitigated through \emph{regularization} techniques \citep{frazin_2000}. In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude. Also new to the present work, is the implementation of an expanded 3D regularization scheme, which adds to the previous scheme a finite difference matrix operator to approximate radial derivatives. In this way, the tomographic inversion problem is performed penalizing nonphysical high-frequency artifacts in all three spatial directions. As a result, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid when compared to previous reconstructions.}
\diego{The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction (covering the height range $1.0-1.25\,\mrsun$) and 2\deg\ in both the latitudinal and longitudinal directions. }

@@

\diego{In this work the cadence of the data time-series was set to 6\,hr and} data from three EUV bands were {used:} 171, 193 and 211 \AA \ in {the} case of AIA, and 171, 195 and 284 \AA \ bands in {the} case of EUVI. When using data from {three bands}, a Gaussian model for the LDEM is able to accurately predict the tomographic emissivities \citep{frazin_2009,nuevo_2015}. In each tomographic voxel the problem is then reduced to finding the values of the three free parameters of the Gaussian (centroid, standard deviation, and area) that allow to best reproduce the three tomographically reconstructed values of FBE in that voxel.

@@

\noindent\notebyalbert{This section will summarize the AWSoM model. Chip, Nishtha, do you think you could provide 2 or 3 paragraphs? We believe the points to cover are:
\begin{itemize}
  \item Data input. Link with the data input for DEMT in terms of dates, etc. One paragraph.
  \item Main physical and technical aspects (grid in particular) of the model.  One paragraph. 
  \item Explain the artificially extended TR. One paragraph.
  \item What are the products of the model we care about in this paper ($N_e$, $T_e$, $B$, $V$, as of now). One paragraph.
\end{itemize}
}

In the transition region {(TR)}, the plasma heats up and becomes less dense {by} several orders of magnitude {over} a short distance. Modeling this region {realistically has a very high computational cost}. For this {reason,} the model uses {an artificially} extended {TR about $\approx 0.05\,\mrsun$ thick, as well as artificially large values for the electronic density and temperature as boundary conditions in $r=1\,\mrsun$.} Consequently, model results below {$\approx 1.05\,\mrsun$} were not taken into account in this article.

The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) is a three-dimensional (3D) physics-based, data-driven model extending from the upper chromosphere, into the solar corona upto 1 AU (and beyond) \citep{vander_2010, Van2014}. AWSoM addresses coronal heating by including the non-linear interaction of forward propagating and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade.
The model accounts for anisotropic (parallel and perpendicular) proton temperatures and isotropic electron temperature. The dissipated turbulent energy is distributed over these three temperatures based on the theories of linear wave damping and stochastic heating. AWSoM does not use ad-hoc heating functions and accounts for both collisional and collision-less electron heat conduction. The Alfv\'{e}n wave number associated with the damping rate is determined by the critical balance condition which uses the cascade time of the minor wave \citep{Lit2007} instead of the previously used cascade time of the major wave \citep{Cha2011, Van2014}. This energy partitioning, in the improved version of AWSoM, leads to more electron heating and less solar wind acceleration \diego{falta cita}%\citep{Van2019b}.
To solve anisotropic MHD equations with radiative cooling, heat conduction and wave turbulence, AWSoM uses the Block-Adaptive-Tree-Solarwind-Roe-Upwind Scheme (BATS-R-US, \citealp{Pow1999, Tot2012}) numerical scheme. MHD equations employed within the AWSoM model are detailed in \citet{Van2014}. Recently, \citet{sachdeva_2019} validated the AWSoM simulation results with a suite of observations from near the Sun upto 1 AU for solar minimum conditions.

Global maps of the observed photospheric magnetic field are essential for accurate modeling of the solar corona and are the primary input for AWSoM. We use the Global Oscillation Network Group (GONG) synoptic map as input for CR2082 (2009-04-05 - 2009-05-03) and the Air Force Data Assimilation Photospheric Flux Transport (ADAPT)-GONG global magnetic field map for CR2208 (2018-09-02 to 2018-09-29). ADAPT-GONG maps are unavailable for CR2082. GONG provides synoptic full disk line-of-sight surface map of the radial magnetic field component. The unobserved polar fields in GONG are estimated by fitting a polynomial to neighboring observed fields. An improvement over these maps is provided by the ADAPT model \citep{Wor2000} which creates synchronic-synoptic maps that uses supergranulation, meridional circulation, flux-transport and differential rotation to evolve the magnetic field on the Sun for better estimates of the unobserved photospheric field \citep{Arg2010, Hen2012}. 
In AWSoM, the 2D radial photospheric field is converted to 3D magnetic field using the Potential Field Source Surface (PFSS) model which specifies the initial condition. We take the source surface to be at 2.5 \rsun and the magnetic field is radial at this height. The radial component specifies the boundary condition.
%ADAPT-GONG maps have multiple realizations based on how the polar fields are filled. We use realization 5 for CR2208.
 Based on \citet{Cha2011} the stochastic heating exponent is taken to be 0.21 and amplitude is 0.18 to account for energy partioning between electrons and protons. The Alfv\'{e}n wave energy boundary condition is given by the poynting flux (S$_{A}$) of the outgoing wave $(\frac{S_{A}}{B})_{\odot} = 1.0\times 10^{6}$ Wm$^{-2}$T$^{-1}$ and the correlation length of the Alfv\'{e}n waves is set to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$ m$\sqrt{T}$.

The base of the transition region forms the inner boundary of the model (at $\approx$1.0\,\rsun). To ensure that the base of the TR is not affected by chromospheric evaporation we overestimate the density at the inner boundary, $N_{e}=N_{i}=N_{\odot}=2\times10^{17}$\,m$^{-3}$ corresponding to the isotropic temperature values, $T_{e}=T_{i}=T_{i\parallel}=T_{\odot}=50,000$\,K. The upper chromosphere is required to extend radially for the density to fall rapidly to correct (lower) values \citep{Lio2009}. In reality, the thin transition has steep gradients in temperature and density as a result of the balance between coronal heating, heat conduction and the radiative losses. To resolve these gradients excessive numerical resources are required. As described in \citet{Lio2009,Sok2013} we artificially broaden the transition region to resolve with our finest grid resolution of $\approx$ 0.001\,\rsun.This results in pushing the corona outwards. At this level, the radiative losses are sufficiently low so that the temperature can increase monotonically with height and form the transition region.
The computational domain for solar corona (SC) extends from 1 to 24 R$_{\odot}$. The spherical grid in SC is radially stretched (with a maximum resolution of 0.001 R$_{\odot}$ near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates. The Adaptive Mesh Refinement (AMR) resolves the angular size to 1.4$^\circ$ between 1 - 1.7 \rsun and 2.8 \rsun outside. The SC component uses about 3 million cells on a $6 \times 8 \times 8$ grid block. Local time stepping is used to speed up the steady state convergence. AWSoM simulation results provide the 3D distribution of density and temperature in addition to the 3D magnetic structure and velocity of the solar wind.

@@

{The energy balance given by Equation (\ref{Balance}) is then integrated in the volume of any given coronal magnetic flux tube. Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal conditon of the magnetic field, a field-line integrated version of that energy balance is found,
\begin{equation}\label{FluxBalance}
\phi_h = \phi_r + \phi_c,
\end{equation}
\noindent
where the line integrated flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},} \\

@@

{Note that, for any given field line, all quantities in these two expresions can be computed from the DEMT and AWSoM models through Equations \ref{Fc}-\ref{Er}. Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line to mantain a stable coronal structure.}
\diego{si vamos a hablar de awsom aca, deberiamos explicar xq no lo analizamos.}

@@

{For both target rotations, Figure \ref{carmaps_R_2082_2208} shows {latitude-longitude} maps of {the DEMT} measure $R$ defined by Equation (\ref{R}), at the same three heights shown in Figures \ref{momento1} and \ref{momento2}. In most of the coronal volume of the DEMT grid the agreement between the tomographic and synthetic FBEs is $\lesssim 1\%$. The notable exception is to be found in the CHs of the target rotation {analysed} based on AIA data. A similar results was found in the two existing DEMT works based on data provided by the AIA instrument \citep{nuevo_2015,maccormack_2017}. This point is further discussed below.}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
\caption{{Carrington maps of the measure $R$ defined by Equation (\ref{R}), for CR-2082 (left panels) and CR-2208 (right panels), at heights $1.025$, $1.065$ and $1.105\,\mrsun$, from top to bottom}. }
\label{carmaps_R_2082_2208}
\end{center}
\end{figure}

{To characterize the DEMT results in different magnetic structures, we traced} $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model. For both rotations, all legss that meet the criteria listed in Section \ref{trace} were selected. For each leg, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}. {As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr\Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.}

>>>>

\begin{abstract}
Observational techniques play an essential role in advancing our understanding of the physics of the solar corona, providing in particular validation data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere. Solar rotational tomography is currently the sole observational technique that provides a 3D quantitative description of the solar corona at a global scale. Based on {extreme ultraviolet} data of space borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$. We carry out a study of the corona combining {DEMT} reconstructions with MHD simulations using the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework. Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the declining} phase of SC 24. The 3D tomographic and MHD models are analysed and compared in distinct coronal magnetic structures. {We report in quantitative detail on the 3D termodinamic structure of the inner corona as revealed by the DEMT analysis. We show in particular the existence of diverse types of temperature structures in the low and mid latitudes of the streamer belt, and that the heating energy required to keep them stable may be accounted for by Alfvén waves. We show that the latest version of the AWSoM model results agree with DEMT reconstructions to within a $\approx 20\%$ accuracy or better. We report on aspects of the AWSoM model that could be improved to better reproduce the DEMT results, in particular concerning the source region of the fast/slow solar winds.}
\end{abstract}

@@

Being the {region} where the solar atmosphere is {heated, solar wind accelerated}, and where impulsive events such as solar flares and coronal mass ejections are energized, observation and modeling of the solar corona are tasks of great relevance to improve our understanding of the Sun-Earth environment. To advance our knowledge of the physics of the solar corona, as well as to improve its three-dimensional (3D) models, information derived from observational data plays a key role. Solar rotational tomography (SRT) is currently the sole observational technique able to provide a quantitative empirical description of the 3D distribution of some fundamental plasma parameters of the solar corona at a global scale.

%\noindent\notebyalbert{Here we will put in a couple of paragraphs summarizing what SRT and DEMT are, including references and defining the accronyms in the process. We should refer to minima in particular. We should mention the instruments and missions we use as data for DEMT, and define their accronyms too. Also one paragraph on the SWMF/AWSoM model, including references and defining the accronyms on the way.}

{To study the global coronal 3D structure, SRT proved to be a powerful tool. Based on solar rotation, allow instruments to compile a time series of images that cover the entire corona collecting data from all lines of sight.} In particular, differential emission measure tomography (DEMT), based on time-series of extreme ultraviolet (EUV) images, allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the {quiet-Sun low corona at a global scale.} The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}. Using solar rotation time series of EUV images taken in channels sensitive to different temperatures, the technique allows calculation of 3D maps of electron density and temperature in the heliocentric height range $1.0\,\mrsun$ to $1.2\,\mrsun$ as summarized in Section \ref{demt}. The reader may refer to the recent review by \citet{vasquez_2016} that summarizes the DEMT technique.

{
A combination of the DEMT and global magnetic models has provided useful insight into the 3D thermodynamical structure of the global quiet-Sun corona. In previous works, DEMT has been combined with a potential field source surface (PFSS) model such as \citet{huang_2012}, \citet{nuevo_2013} and \citet{nuevo_2015}. Recently, \citet{lloveras_2017} combined DEMT with PFSS to study the thermodynamic of the last two solar minima along magnetic field lines and selecting different magnetic structures and \citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona throgh PFSS magnetic lines.}

{The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) is a three-dimensional (3D) physics-based, data-driven model extending from the upper chromosphere, into the solar corona upto 1 AU (and beyond) \citep{vander_2010, Van2014} and is constantly validated with observations as new improvements are implemented. DEMT results were used by \citet{jin_2012} and \citet{oran_2015} to validate AWSoM results finding an agreement within 50\% in density and electron temperature in the low corona. More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT products in a globally fashion, obtaining an agreement within 20\%.
We used AWSoM results with two purposes. On the one hand to provide thermodynamic results to be contrasted with DEMT, and on the other hand to provide magnetohydrodynamic (MHD) coronal magnetic field model that is used to study thermodynamics along field lines.
}

We carry out a quantitatively detailed comparative {DEMT/AWSoM} analysis of the Carrington Rotation (CR)-2082 during the Solar Cycle (SC) 23/24 minimum and CR-2208 during the declining fase of SC 24. To study CR-2082 data taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B \citep{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) was used {for DEMT, and Global Oscillation Network Group (GONG) magnetogram as the only input for AWSoM}, while data taken by the \textit{Atmospheric Imaging Assembly instrument} {(AIA \citep{lemen_2012})}, on board the \textit{Solar Dynamics Observatory} (SDO) mission was used to study CR-2208 {for DEMT, and Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG magnetograms for AWSoM}.

{
Section \ref{demt} and \ref{awsom} summarizes DEMT technique, AWSoM model, instruments, and datasets we used. Section \ref{trace} explains the technique that is used to trace the thermodynamic results along the field lines. Section \ref{energia} details the energy model and the loop integrated quantities that are part of the comparative analysis. In Section \ref{demt_res} the quantitative comparative analysis of both rotations using DEMT is described and in Section \ref{awsom_res} AWSoM results are related to the one of DEMT. Finally in Section \ref{discu} summarizes and discusses the main conclusions of this analysis, and anticipates further planned work.
}
\\
%{El parrafo de abajo lo pondria en la seccion 2.1}\\
%In DEMT, the low corona in the height range $1.0-1.25\,\mrsun$ is discretized in a spherical computational grid. The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions. The cadence of the data time-series is set to 6\,hr. The main product of the technique is the local DEM (LDEM) at each volxel, a measure of the temperature distribution of the plasma contained in it.

@@

{The solution of the tomographic problem involves a very large sparse matrix. Such type of inversion problems are characterized by spurious high-frequency artifacts in the solution, which can be mitigated through \emph{regularization} techniques \citep{frazin_2000}. In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude. Also new to the present work, is the implementation of an expanded 3D regularization scheme, which adds to the previous scheme a finite difference matrix operator to approximate radial derivatives. In this way, the tomographic inversion problem is performed penalizing nonphysical high-frequency artifacts in all three spatial directions. As a result, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid when compared to previous reconstructions.}
{The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction (covering the height range $1.0-1.25\,\mrsun$) and 2\deg\ in both the latitudinal and longitudinal directions. }

@@

{In this work the cadence of the data time-series was set to 6\,hr and} data from three EUV bands were {used:} 171, 193 and 211 \AA \ in {the} case of AIA, and 171, 195 and 284 \AA \ bands in {the} case of EUVI. When using data from {three bands}, a Gaussian model for the LDEM is able to accurately predict the tomographic emissivities \citep{frazin_2009,nuevo_2015}. In each tomographic voxel the problem is then reduced to finding the values of the three free parameters of the Gaussian (centroid, standard deviation, and area) that allow to best reproduce the three tomographically reconstructed values of FBE in that voxel.

@@

%\noindent\notebyalbert{This section will summarize the AWSoM model. Chip, Nishtha, do you think you could provide 2 or 3 paragraphs? We believe the points to cover are:
%\begin{itemize}
%  \item Data input. Link with the data input for DEMT in terms of dates, etc. One paragraph.
%  \item Main physical and technical aspects (grid in particular) of the model.  One paragraph. 
%  \item Explain the artificially extended TR. One paragraph.
%  \item What are the products of the model we care about in this paper ($N_e$, $T_e$, $B$, $V$, as of now). One paragraph.
%\end{itemize}
%}

%In the transition region {(TR)}, the plasma heats up and becomes less dense {by} several orders of magnitude {over} a short distance. Modeling this region {realistically has a very high computational cost}. For this {reason,} the model uses {an artificially} extended {TR about $\approx 0.05\,\mrsun$ thick, as well as artificially large values for the electronic density and temperature as boundary conditions in $r=1\,\mrsun$.} Consequently, model results below {$\approx 1.05\,\mrsun$} were not taken into account in this article.

%The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) is a three-dimensional (3D) physics-based, data-driven model extending from the upper chromosphere, into the solar corona upto 1 AU (and beyond) \citep{vander_2010, Van2014}.

AWSoM addresses coronal heating by including the non-linear interaction of forward propagating and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade.
The model accounts for anisotropic (parallel and perpendicular) proton temperatures and isotropic electron temperature. The dissipated turbulent energy is distributed over these three temperatures based on the theories of linear wave damping and stochastic heating. AWSoM does not use ad-hoc heating functions and accounts for both collisional and collision-less electron heat conduction. The Alfv\'{e}n wave number associated with the damping rate is determined by the critical balance condition which uses the cascade time of the minor wave \citep{Lit2007} instead of the previously used cascade time of the major wave \citep{Cha2011, Van2014}. This energy partitioning, in the improved version of AWSoM, leads to more electron heating and less solar wind acceleration.% \diego{falta cita}%\citep{Van2019b}.
To solve anisotropic MHD equations with radiative cooling, heat conduction and wave turbulence, AWSoM uses the Block-Adaptive-Tree-Solarwind-Roe-Upwind Scheme (BATS-R-US, \citealp{Pow1999, Tot2012}) numerical scheme. MHD equations employed within the AWSoM model are detailed in \citet{Van2014}. Recently, \citet{sachdeva_2019} validated the AWSoM simulation results with a suite of observations from near the Sun upto 1 AU for solar minimum conditions.

Global maps of the observed photospheric magnetic field are essential for accurate modeling of the solar corona and are the primary input for AWSoM. The model use GONG synoptic map as input for CR-2082 (2009-04-05 - 2009-05-03) and ADAPT-GONG global magnetic field map for CR-2208 (2018-09-02 to 2018-09-29). ADAPT-GONG maps are unavailable for CR-2082. GONG provides synoptic full disk line-of-sight surface map of the radial magnetic field component. The unobserved polar fields in GONG are estimated by fitting a polynomial to neighboring observed fields. An improvement over these maps is provided by the ADAPT model \citep{Wor2000} which creates synchronic-synoptic maps that uses supergranulation, meridional circulation, flux-transport and differential rotation to evolve the magnetic field on the Sun for better estimates of the unobserved photospheric field \citep{Arg2010, Hen2012}. 
In AWSoM, the 2D radial photospheric field is converted to 3D magnetic field using the PFSS model which specifies the initial condition. We take the source surface to be at $2.5 \, \mrsun$ and the magnetic field is radial at this height. The radial component specifies the boundary condition.
%ADAPT-GONG maps have multiple realizations based on how the polar fields are filled. We use realization 5 for CR2208.
Based on \citet{Cha2011} the stochastic heating exponent is taken to be 0.21 and amplitude is 0.18 to account for energy partioning between electrons and protons. The Alfv\'{e}n wave energy boundary condition is given by the poynting flux (S$_{A}$) of the outgoing wave $(\frac{S_{A}}{B})_{\odot} = 1.0\times 10^{6}$ Wm$^{-2}$T$^{-1}$ and the correlation length of the Alfv\'{e}n waves is set to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$ m$\sqrt{T}$.

The base of the transition region (TR) forms the inner boundary of the model (at $\approx$1.0\,\rsun). To ensure that the base of the TR is not affected by chromospheric evaporation we overestimate the density at the inner boundary, $N_{e}=N_{i}=N_{\odot}=2\times10^{17}$\,m$^{-3}$ corresponding to the isotropic temperature values, $T_{e}=T_{i}=T_{i\parallel}=T_{\odot}=50,000$\,K. The upper chromosphere is required to extend radially for the density to fall rapidly to correct (lower) values \citep{Lio2009}. In reality, the thin transition has steep gradients in temperature and density as a result of the balance between coronal heating, heat conduction and the radiative losses. To resolve these gradients excessive numerical resources are required. As described in \citet{Lio2009,Sok2013} we artificially broaden the transition region to resolve with our finest grid resolution of $\approx$ 0.001\,\rsun. This results in pushing the corona outwards. At this level, the radiative losses are sufficiently low so that the temperature can increase monotonically with height and form the transition region. Consequently, AWSoM results below {$\approx 1.05\,\mrsun$} were not taken into account in this article.
\\
The computational domain for solar corona extends from 1 to 24 R$_{\odot}$. The spherical grid is radially stretched (with a maximum resolution of $0.001 \, \mrsun$ near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates. The Adaptive Mesh Refinement resolves the angular size to 1.4$^\circ$ between $1 - 1.7 \, \mrsun$ and $2.8 \, \mrsun$ outside. The solar corona component uses about 3 million cells on a $6 \times 8 \times 8$ grid block. Local time stepping is used to speed up the steady state convergence. AWSoM simulation results provide the 3D distribution of density and temperature in addition to the 3D magnetic structure and velocity of the solar wind.

@@

{The energy balance given by Equation \ref{Balance} is then integrated in the volume of any given coronal magnetic flux tube. Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal conditon of the magnetic field, a field-line integrated version of that energy balance is found,
\begin{equation}\label{FluxBalance}
\phi_h = \phi_r + \phi_c,
\end{equation}
\noindent
where the line integrated flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},} \\

@@

{Note that, for any given field line, all quantities in these two expresions can be computed {from DEMT model} through Equations \ref{Fc}-\ref{Er}. Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line to mantain a stable coronal structure.}

@@

{For both target rotations, Figure \ref{carmaps_R_2082_2208} shows {latitude-longitude} maps of {the DEMT} measure $R$ defined by Equation \ref{R}, at the same three heights shown in Figures \ref{momento1} and \ref{momento2}. In most of the coronal volume of the DEMT grid the agreement between the tomographic and synthetic FBEs is $\lesssim 1\%$. The notable exception is to be found in the CHs of the target rotation {analysed} based on AIA data. A similar results was found in the two existing DEMT works based on data provided by the AIA instrument \citep{nuevo_2015,maccormack_2017}. This point is further discussed below.}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
\caption{{Carrington maps of the measure $R$ defined by Equation \ref{R}, for CR-2082 (left panels) and CR-2208 (right panels), at heights $1.025$, $1.065$ and $1.105\,\mrsun$, from top to bottom}. }
\label{carmaps_R_2082_2208}
\end{center}
\end{figure}

Figure 1 shows the ADAPT-GONG and GONG global
maps for CR2208. The two maps show significant dif-
ferences, especially in the polar regions. We find that
using ADAPT-GONG maps as input to the AWSoM
model produces significantly better results in compar-
ison to using GONG maps. Therefore, in this work
we use ADAPT-GONG global magnetic maps for both
CR2208 and CR

Figure \ref{Br} shows carrington maps of radial magnetic field ($Br$) for both rotations at $1.005\, \mrsun$. Both maps show a clear dipole. The main difference is observed in the polar region and is due to the different types of approaches that use GONG (CR-2082) and ADAPT-GONG (CR-2208.)

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/map_Br_awsom_2082_185_extend_1005_Rsun.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/map_Br_awsom_2208_185_extend_1005_Rsun.pdf}
\caption{Carrington maps of radial magnetic field obtained with AWSoM at $1.005 \, \mrsun$ for CR-2082 (left) and CR-2208 (right). }
\label{Br}
\end{center}
\end{figure}

{To characterize the DEMT results in different magnetic structures, we traced} $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model. For both rotations, all legs that meet the criteria listed in Section \ref{trace} were selected. For each leg, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}. {As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr\Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.}
